Quantifying the home ground advantage

### 2022-07-11 inst/home_advantage.Rmd
hyper3 analysis of home advantage

>>>>

# hyper3 idiom

We may apply `hyper3` idiom to the dataset. First a formal test:

```{r,label=optimizebaseball,cache=TRUE}
baseball_table
f <- function(l){ maxp(home_away3(baseball_table,l),give=TRUE,n=1)$likes}
o <- optimize(f,c(0.8,1.6),maximum=TRUE)
o
maxL <- f(o$maximum)
W <- maxL - f(1)    # f(1) being the likelihood of the null
W
pchisq(2*W,df=1,lower.tail=FALSE)
```

The pvalue is significant.  Now plot a profile likelihood (support)
curve:

```{r, label=hyper3_baseball,cache=TRUE}
jj1  <- seq(from=log(o$maximum),to=log(1.9),len=7)
jj2  <- seq(from=log(o$maximum),to=log(0.8),len=7)
l <- sort(unique(exp(c(jj1,jj2))))
lam  <- sort(c(l,o$maximum))
L <- sapply(lam,f) - maxL
```

```{r,label=plothyper3baseball}
plot(log(lam),L,type="b")
abline(h=c(0,-2))
abline(v=0)

plot(lam,L,type="b")
abline(h=c(0,-2))
```
